\documentclass[12pt,a4paper]{article}
\textheight=230mm
\textwidth=140mm
\headsep=20mm
\columnsep=5mm

\setlength{\hoffset}{-2cm}
\setlength{\voffset}{-2cm}
\topmargin=1.5cm
\oddsidemargin=2cm
\evensidemargin=1.5cm
\textwidth=17cm
\textheight=23cm
\raggedbottom
\sloppy

%\DisemulatePackage{setspace}
\usepackage{setspace}

\usepackage{amsmath}
\usepackage[utf8x]{inputenc}
\usepackage{color}

\usepackage{tikz}
\usepackage{circuitikz}
\usetikzlibrary{circuits}
\usetikzlibrary{circuits.ee}
\usetikzlibrary{circuits.ee.IEC}
\usetikzlibrary{circuits.logic.IEC}

\usepackage{epstopdf}

\usepackage{graphicx}
\usepackage{subfig}
\usepackage{tikz-cd}
\usetikzlibrary{decorations.pathmorphing}

\usepackage{lineno}

\usepackage{url}

\author{Bereziuk~Ivan}
\graphicspath{ {img/} }

\def\mean#1{\left< #1 \right>}


\title{ Preliminary design studies of a drift tube detector for SHiP experiment }

\begin{document}
	 \linenumbers
	\maketitle
	\newpage
	
%	\tableofcontents	
		
%	\begin{spacing}{1}
	\input{introduction/intro}
%	\end{spacing}	

	\input{SubjectOfStudy}

	\input{Signal}
	
	\input{Gain}		 

	\include{sag/sag}
	
	\include{track_reconstruction/track_reconstruction}	
	
	\include{Measurements}
	
\newpage
\section{Appendix}

\subsection{pressure meter}

	For the pressure measurement inside of drift tube we used pressure transmitters from SensorTechnics$^{\textregistered}$. The devise is marked by ID:CTE9005AQ4, so we used appropriate datasheet  from the manufacturer \cite{presTransmitDatasheet}.
	
	According to datasheet and marking, this pressure transmitter is designed for pressure measurements in the interval $0 \dots 5~bar$. But on the transmitter is marked an interval $0\dots 3,5~bar$. So to be able to use this device, we additionally calibrated it.
	
	For this purpose we used two control points: the output current value for atmospheric pressure at that point (727 mmHg) and a current for a vacuum. To get a vacuum we used a pump which decreases a pressure to the value  $<0.001~bar$ which we consider as a vacuum.
	
%	Для вимірювання тиску в дрейфовій трубці використовувався датчик тиску(pressure transmitters) від компанії SensorTechnics$^{\textregistered}$. На приладі зазначено ідентифікаційний код ID:CTE9005AQ4, по якому було знайдено відповідну документацію від виробника \cite{presTransmitDatasheet}.

%	Згідно до документації та маркування, даний прилад розрахований на вимірювання тиску в діапазоні від $0 \dots 5~bar$. Проте безпосередньо на самому манометрі вказаний діапазон $0\dots 3,5~bar$. Тож для використання даного приладу ми вдалися до додаткової калібровки.
	
%	Для досягнення даної цілі було використано 2 контрольні точки: показник струму для атмосферного тиску в даний момент, і струм для вакууму. Для досягнення вакууму була використана помпа що понижувала тиск до значення $<0.001~bar$ що можна вважати за вакуум.
	
	\begin{table}[!h]
	\centering
	\caption{ Control points for calibration of pressure transmitter.}
	\begin{tabular}{|l|l|}
		\hline
		pressure [bar] & voltage[V] \\
		\hline
		$<0.001$ & 0.405\\
		\hline
		1 & 0.858\\
		\hline
	\end{tabular}
	\end{table}
	
	Therefore the voltage dependence taken on a resistor 	$100\Omega$ depends on a pressure as:
%	Таким чином залежність напруги що знімається на резистрорі $100\Omega$ залежить від тиску по закону:
	\begin{equation}
	V = 4.05 + 0.453 \cdot P[bar]
	\end{equation}

	\begin{equation}	
	P[bar] = -0.894 + 2.2075 \cdot V
	\end{equation}

\newpage
\begin{thebibliography}{00}	
		
	\bibitem{NA62_TDR} F. Hahn, F. Ambrosino, A. Ceccucci, H. Danielsson, N. Doble, F. Fantechi, A. Kluge, C. Lazzeroni, M. Lenti, G. Ruggiero, M. Sozzi, P. Valente, and R. Wanke. NA62: Technical Design Document. Technical Report NA62-10-07, CERN, Geneva
	
	\bibitem{ship_TP} SHiP Technical Proposal from 8 april 2015: arXiv:1504.04956v1
	
	\bibitem{garfield} GARFIELD tutorial \url{http://garfield.web.cern.ch/garfield}
	
	\bibitem{kozlinskiy} Outer Tracker calibration and open charm production cross section measurement at LHCb, 2013 A.V.Kozlinskiy. \\  \url{http://dspace.ubvu.vu.nl/bitstream/handle/1871/40430/dissertation.pdf}
	
	\bibitem{presTransmitDatasheet} DataSheet for Pressure transmitters for corrosive liquids and gases CTE/CTU9000 series. \url{http://www.first-sensor.com/cms/upload/datasheets/DS_Standard-CTE-CTU9000_E_11509.pdf}
	
	\bibitem{EoI} W. Bonivento, A. Boyarsky, H. Dijkstra, U. Egede, M. Ferro-Luzzi, B. Goddard, A. Golutvin, D. Gorbunov, R. Jacobsson, J. Panman, M. Patel, O. Ruchayskiy, T. Ruf, N. Serra, M. Shaposhnikov, and D. Treille. Proposal to Search for Heavy Neutral Leptons at the SPS. Technical Report CERN-SPSC-2013-024. SPSC-EOI-010, CERN, Geneva (Oct, 2013).
	
\end{thebibliography}
	
\end{document}
